Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2014-10-02 FrontMatter/Abstract.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

\begin{abstract}

Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications. Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes. To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established. This Ph.D. study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures. This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures. This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.

>>>>

\begin{abstract}
Transition metal oxides (TMOs) exhibit rich structures and useful properties, and could been used in solar energy harvesting (\emph{e.g.}, photoelectrochemistry, photocatalysis, and photovoltaics) and energy saving (\emph{e.g.}, electrochromism and photochromism) applications. Nano-engineering of these TMOs could produce a variety of nanostructures, modify the electronic and optical properties, potentially enhance the performances and extend their applications into new regimes. To fully harvest the advantages of these materials, a scalable growth method and a comprehensive understanding towards the growth-structure-property relation must be established. This Ph.D. study focused on one-dimensional (1D) tungsten trioxide (\ce{WO3}) and molybdenum trioxide (\ce{MoO3}) nanostructures. This dissertation synthesized 1D \ce{WO3} and \ce{MoO3} nanostructures using chemical vapor deposition (CVD) approach, characterized the morphologies and structures, and measured the optical properties of the as-prepared nanostructures. This study aims at accomplishing controlled and scalable growth of \ce{WO3} and \ce{MoO3} using CVD method, establishing the structure-property relations to rationalize nanostructure synthesis for energy applications, and presenting preliminary results on the devices assembled using the \ce{WO3} and \ce{MoO3} nanostructures.

### 2014-10-02 ch-moox/moox.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

In this chapter,

>>>>

In this chapter, a new growth model of \ce{MoO3} using alkaline metal ions as catalysts was discovered and investigated in depth. The growth kinetics was closely inspected using a series of controlled experiments. A modified vapor-solid-solid mechanism was proposed and favorably verified. Two growth modes, i.e., transverse growth and axial growth, were highlighted, which not only improved the yield, but also allowed for versatile morphology control of 1D \ce{MoO3} nanostructures. This methodology was further extended onto glass and ITO glass substrates, paving the way to a more integrated process of using \ce{MoO3} nanostructures onto various solar energy saving and harvesting applications.

### 2014-10-02 ch-tms/tms.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

\chapter{WO$_3$-WS$_2$ Heterostructure}

@@

Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, and sulfur powder was used to fabricate \ce{WO3}-\ce{WS2} core-shell NWs, as summarized in Table.~\ref{tab:ch5pre}. All reactants were employed as received without further processing. Substrates cleaning procedures have been introduced in Sec.~\ref{ch2sub}.

% Tungsten powders size and purity
\begin{table}[htb]
\centering
\caption{List of reactants for \ce{WO3}-\ce{WS2}}\label{tab:ch5pre}
\begin{tabular}{lccr}
\toprule
Name & purity & average size & vendor info\\
\midrule
3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
3N5   &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
4N5   &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
\bottomrule
\end{tabular}
\end{table}

\ce{WO3} NWs were obtained by a seeded growth with tungsten powders applied onto the Si substrate. To find out the optimal conditions, tungsten powder oxidation experimental were carried out. Schematic layout of each growth were illustated in Fig.~\ref{fig:ch5grow} including the sulfurization process.

@@

The morphology of \ce{WO3} NWs in micron scale almost stay the same after sulfurization, as shown in the inset SEM imaging of Fig.~\ref{fig:ch5ws2sem}. The length of individual nanowire can be up to 15 $\mu$m and the diameter varies from about 40 to 300 nm. The surface of the NWs were rather smooth without other attachments. The NWs array grow slightly larger than the W seed ( $\sim 12 \mu$m), mostly due to the elongation of NW.

@@

%fig xrd ws2 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_cs_xrd}
\caption[XRD on core-shell NWs]{X-ray diffraction spectra before and after sulfurization. The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
\label{fig:ch5ws2xrd}
\end{figure}

This observation can also be used to account for the extreme small peak at 13.87$^{\circ}$ in the post-sulfurization spectrum. Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), this redshift indicates an increase of lattice spacing along $c$ axis (from 6.16 \AA to 6.38 \AA). The FWHM of this (002) peak is about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.

Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs. Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively. A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization. The measured layer spacing is 6.4 \AA, slight larger than bulk 2H-\ce{WS2} of 6.16 \AA, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}. The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.

% tem core shell layer
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
\caption[TEM imaging on core-shell NWs: 1]{HRTEM imaging on one core-shell nanowire showing layer number changes.}
\label{fig:ch5ws2tem1}
\end{figure}

After examining dozens of core-shell NWs, this thesis found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}

@@

>>>>

\chapter{TEM-RAMAN STUDY ON INDIVIDUAL TUNGSTEN OXIDE-TUNGSTEN DISULFIDE CORE-SHELL NANOWIRE}

@@

The \ce{WO3}-\ce{WS2} core-shell nanowires were fabricated using a sulfurization process based on the \ce{WO3} NWs prepared by the seeded growth method in Chapter~3, Sec.~\ref{sec:sgfg}. For the sake of completeness, schematic layout of overall growth were illustrated in Fig.~\ref{fig:ch5grow} including the oxidation of W powder, the seeded growth and the sulfurization process.

@@

The morphology of \ce{WO3} NWs in micron scale almost stay the same after sulfurization, as shown in the inset SEM imaging of Fig.~\ref{fig:ch5ws2sem}. The length of individual nanowire can be up to 15 $\mu$m and the diameter varies from about 40 to 300 nm. The surface of the NWs were rather smooth without other attachments. The NWs array grow slightly larger than the W seeds ($\sim$12 $\mu$m), mostly due to the elongation of NW.

@@

%fig xrd ws2 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_cs_xrd}
\caption[XRD on core-shell NWs]{X-ray diffraction spectra before and after sulfurization. The reference spectra for $c$-W, 2H-\ce{WS2} and $m$-\ce{WO3} are included with some major peaks labeled.}
\label{fig:ch5ws2xrd}
\end{figure}
This observation can also be used to account for the extreme small peak at 13.87$^{\circ}$ in the post-sulfurization spectrum. Compared the reference 2H-\ce{WS2} (002) peak (14.37$^{\circ}$, ICDD PDF 04-003-4478), the redshift of sample peak indicates an increase of lattice spacing along $c$ axis (from 6.16 \si{\angstrom} to 6.38 \si{\angstrom}). The FWHM of this (002) peak is about 1.1$^{\circ}$, giving an estimation on the crystalline size of 7.5 nm according to Scherrer equation.

Due to this small spacing, TEM is primarily utilized to observe the detailed morphology of \ce{WO3}-\ce{WS2} core-shell NWs. Fig.~\ref{fig:ch5ws2tem1} shows HRTEM imaging on typical tip and body region of the core-shell NW, respectively. A comparison with the pre-sulfurization specimen (Fig.~\ref{fig:woseedtem2} on page~\pageref{fig:woseedtem2}) readily reveals the formation of core-shell morphology after sulfurization. The measured layer spacing is 6.4 \AA, slight larger than bulk 2H-\ce{WS2} of 6.16 \AA, but in good agreement with XRD results in Fig.~\ref{fig:ch5ws2xrd}. The clear contrast in core region also prove the lattice structure of \ce{WO3} is not seriously distorted.

% tem core shell layer
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{ws2_coreshell_tem}
\caption[TEM imaging on core-shell NWs: 1]{HRTEM imaging on one core-shell nanowire showing layer number changes.}
\label{fig:ch5ws2tem1}
\end{figure}
After examining dozens of core-shell NWs, it was found the \ce{WS2} layer number at NW tip was usually the largest, reaching more than ten, and the layer number could decrease to one along the NW body, but there exist some layer number fluctuation and shape modification. Fig.~\ref{fig:ch5ws2tem3} shows a smooth transition of \ce{WS2} layer number on the tip region of one NW. The layer number is about 7 on the tip corner, gradually decreases from 4 to 3 along the NW body, and stops at 2. Closer observation indicates the layer spacing is not quite uniform in the tip area, probably due to the complex curvature and bending. \ce{WS2} fullerene also show similar structures. Since the closing of the tip region could be of great complexity and the induced strain could modify Raman signal considerably, the TEM-Raman integrated measurement in this study will focus on the body region only, with those having smooth transition of layer number.
% coreshell tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_growth3}
\caption[TEM imaging on core-shell NWs: 2]{HRTEM imaging on the tip area of one core-shell nanowire.}
\label{fig:ch5ws2tem3}
\end{figure}

@@

A comprehensive understanding of the structure-property relation, which is essential to successful application of nanomaterials, is often hindered by the ensemble averaged characterizations in conventional methods. The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates. And considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer \ce{WS2} nanotube was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified. These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications. More important, this technique of TEM-Raman integrated study could be readily applied to a variety of other nanomaterials, therefore opening a broad spectrum for the understanding of the structure-property relation, propelling the potential nano-engineering applications.

\chapter{SUMMARY AND FUTURE WORK}

### 2014-10-02 ch-wox/ch-wox.tex
temperatory fix for multiline chapter name display in ToC
after format review, bold font in figure caption removed, frontmatter spacing fixed

\chapter{Impurity Effects on WO$_3$ Nanowires}

@@

The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition. The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition. Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5. The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases. Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5. And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases. These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b).

@@

The optical transmission and reflection properties of the as-grown \ce{Na5W14O44} NWs were evaluated using UV-Vis spectroscopy, as shown in Fig.~\ref{fig:ch3naxuvvis}. The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm. SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate. 
%051412 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:nauv}\includegraphics[width=0.45\textwidth]{uvvis_naxwo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
\caption[UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz]{(a) Optical transmission and (b) diffuse reflection spectra of \ce{Na5W14O44} NWs on quartz.}
\label{fig:ch3naxuvvis}
\end{figure}
The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength. This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm. One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm. The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting a bandgap edge at about 380 nm. This is consistent with the observed white sample color; however, the \ce{Na5W14O44} should be metallic in theory. More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW. 
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}
Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively. The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end. The exact dimension still shows some minor difference, particularly in low temperature region. The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature. Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown hereby.}
\label{fig:wox4n5}
\end{figure}
It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 (Fig.~\ref{fig:wox4n5}c), although not in large scale.

@@

Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth. Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius} ) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare. This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure. It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature. It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth. This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.

@@

Two interesting approaches for \ce{WO3} NW growth were found during this study, both of which can produce \ce{WO3} NWs with its own merit. The first one is related to the vapor flow dynamic in the deposition region. As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 in long. However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region. For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1. W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure. Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b. However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber. The NW density is dramatically increased. The NWs have length about 1 to 2 $\mu m$ and diameter about 200 nm. Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
% fg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:fg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:fg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
\label{fig:wogrowsf}
\end{figure}
The growth mechanism here can be explained by aforementioned VS process as well. Both local flow and temperature play an vital role in the formation of dense NW array. Splitting one substrate into two presumably introduces some fluctuation in the vapor flow. It is well known that in lamellar flow region, there is a velocity boundary above the side wall. In spite of the high crystalline quality, the \ce{WO3} is not long enough and yield is limited by the evaporation of source materials; therefore this approach is not seriously pursued in this study.

%TEM to be done on D8.
% fg tem
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
%\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
%\label{fig:fgtem}
%\end{figure}

@@

to be added, NaOH WO3 results. 
A systematical investigation of \ce{WO3} NW growth using W powders as precursor in CVD method was performed.

>>>>

\chapter{IMPURITY EFFECTS ON THE GROWTH OF TUNGSTEN OXIDE NANOWIRES}

@@

The general trend of Na/W ratios with the growth number can also be explained by the aforementioned effect of residue deposition. The sodium contents from the residue deposition will join the new Na contents from the W source forming deposition. Fig.~\ref{fig:nawoxxrd} displays the XRD spectra of a series of specimens with the growth number increases from 1 to 5. The XRD spectra reveal the relative concentration dynamics of the three phases as the growth number increases. Compared to the \ce{WO3} phase, the \ce{Na5W_{14}O_{44}} and the \ce{Na2W4O_{13}} phases increase significantly as the growth number increase from 1 to 5. And in the 5th growth, \ce{Na2W4O_{13}} become the dominated phase compared to the other two phases. These results are consistent with the SEM observation (Fig.~\ref{fig:nawoxsemall}) and the composition change from the EDX measurements (Fig.~\ref{fig:nawoxser}b). Details XRD indices assignment is summarized in Table~\ref{tbl:xrd}.

\begin{table}
\centering
\caption{XRD assignments}\label{tbl:xrd}
\begin{tabular}{llllll}
\toprule
\ce{WO3} &          &\ce{Na5W14O44} &      & \ce{Na2W4O13} & \\
2$\theta$   & hkl   & 2$\theta$   & hkl    & 2$\theta$   & hkl   \\
\midrule
 23.05   & 0 0 2 & 9.65    & 0 0 2  & 10.85   & 1 0 0 \\
 23.59   & 0 2 0 & 14.49   & 0 0 3  & 21.8    & 2 0 0 \\
 24.31   & 2 0 0 & 19.37   & 0 0 4  & 32.97   & 3 0 0 \\
 26.60   & 1 2 0 & 24.27   & 0 0 5  & 56.45   & 5 0 0 \\
 34.10   & 2 0 2 & 29.22   & 0 0 6  &         &       \\
 47.11   & 0 0 4 & 39.36   & 0 0 8  &         &        \\
 48.29   & 0 4 0 & 44.46   & 0 0 9  &         &        \\
 49.79   & 4 0 0 & 49.71   & 0 0 10 &         &        \\
         &       & 55.23   & 0 0 11 &         &        \\
         &       & 60.77   & 0 0 12 &         &        \\
\bottomrule
\end{tabular}
\end{table}

@@

The optical transmission and reflection properties of the as-grown \ce{Na5W14O44} NWs were evaluated using UV-Vis spectroscopy, as shown in Fig.~\ref{fig:ch3naxuvvis}. The sample was prepared on a quartz substrate, which is transparent from 300 to 1300 nm. SEM images (not shown) found dense NWs array growth similar to those on \ce{SiO2}-Si substrates, indicating the residue effect is not sensitive to the substrate. 
%051412 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:nauv}\includegraphics[width=0.45\textwidth]{uvvis_naxwo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:nadrs}\includegraphics[width=0.45\textwidth]{uvvis_naxwo2}}
\caption[UV-Vis and DRS of \ce{Na5W14O44} NWs on quartz]{(a) Optical transmission and (b) diffuse reflection spectra of \ce{Na5W14O44} NWs on quartz.}
\label{fig:ch3naxuvvis}
\end{figure}
The transmission (Fig.~\ref{fig:nauv}) was about 70\% above 400nm, and began to drop significantly for shorter wavelength. This variation was also identified in the diffuse reflection spectrum in Fig.~\ref{fig:nadrs}, where the reflection reached to a maximum of 16\% at 390 nm. One difference is the DRS increased from 1300 nm to 400nm, presumably due to the inverse scattering intensity with NW dimension of 300 nm. The calculated absorption was shown in Fig.~\ref{fig:nauv}, suggesting a bandgap edge at about 380 nm. This is consistent with the observed white sample color; however, the \ce{Na5W14O44} should be metallic in theory. More investigation is needed to vigorously determined the electronic transport properties of \ce{Na5W14O44} NW. 
\textbf{Ordinary transport growth using other W powders}
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}

Typical morphologies of ordinary transport growth using other powders are shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively. The common feature of these samples is the dominance of islands growth in upstream end and layers growth in downstream end. The exact dimension still shows some minor difference, particularly in low temperature region. The deposition with 4N5 and 5N have much smaller grain size than that with 3N5 powder.
% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature. Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown hereby.}
\label{fig:wox4n5}
\end{figure}
It is worth pointing out that there are some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.

@@

Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth. Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare. This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure. It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature. It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth. This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.

@@

Two interesting approaches for \ce{WO3} NW growth were found during this study, both of which can produce \ce{WO3} NWs with its own merit. The first one is related to the vapor flow dynamic in the deposition region. As shown in Sec.~\ref{sec:nawox}, ordinary transport growth using high purity W power mostly leads to thin film growth on one substrate of 1 in long. However, it was found that when two shorter substrates were closely placed together, the \ce{WO3} NW yield was significantly enhanced in the second substrate located in lower temperature region. For instance, substrate 1 (Sub1) is located at 6.75 to 7 inch (Fig.~\ref{fig:wogrow} horizontal axis on page~\pageref{fig:wogrow}), and substrate 2 (sub2) is placed in close vicinity of downstream end of sub1. W source moves to 5 inch, and 0.3 sccm \ce{O2} is used to reduce the \ce{WO_x} vapor pressure. Deposition on sub1 is characterized by thin film, similar to those shown in Fig.~\ref{fig:wox4n5}b. However, deposition on sub2 (Fig.~\ref{fig:fg1}) is in sharp contrast to that shown in Fig.~\ref{fig:wox4n5}c, although they are both located in the low temperature region of reaction chamber. The NW density is dramatically increased. The NWs have length about 1 to 2 $\mu$m and diameter about 200 nm. Close-up view (inset of Fig.~\ref{fig:fg2}) shows the NWs have clear facets, implying its high crystalline quality.
% fg sem
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:fg1}\includegraphics[width=0.45\textwidth]{wox_flow1}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:fg2}\includegraphics[width=0.45\textwidth]{wox_flow2}}
\caption[Characterization of flow growth \ce{WO3}: SEM]{ (a) Low magnification SEM image showing dense array of NWs (b) High magnification SEM image of NWs grew out of layer and close-up view on individual wire.}
\label{fig:wogrowsf}
\end{figure}
The growth mechanism here can be explained by aforementioned VS process as well. Both local flow and temperature play an vital role in the formation of dense NW array. Splitting one substrate into two presumably introduces some fluctuation in the vapor flow. It is well known that in lamellar flow region, there is a velocity boundary above the side wall. In spite of the high crystalline quality, the \ce{WO3} is not long enough and yield is limited by the evaporation of source materials; therefore this approach is not seriously pursued in this study.

%TEM to be done on D8.
% fg tem
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.8\textwidth]{wo3_tem.jpg}
%\caption[Flow growth of \ce{wo3}:TEM]{TEM characterization of FG \ce{WO3} NWs. }
%\label{fig:fgtem}
%\end{figure}
to be added, NaOH WO3 results.

@@

A systematical investigation of \ce{WO3} nanowire growth using CVD method with tungsten powders as precursor was performed. Four kinds of tungsten powder sources were used, and the sodium impurity effect was throughly studied. \ce{Na5W14O44} NW was first reported from this study; the crystal structure was investigated in details, and HRTEM images were obtained. Besides, the Raman vibrational spectroscopy of \ce{Na5W14O44} was also revealed. The presence of sodium tungsten oxide phase indicates that the CVD growth of \ce{WO3} is extremely sensitive to Na contents. The insight of \ce{WO3} growth kinetics we have gained from this study could help establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions, thereby turning this deleterious effect into a beneficial approach of controlled growth. In fact, favorable results have been observed on both \ce{WO3} and \ce{MoO3} 1D nanostructures syntheses using NaOH treated Si substrates. Details will be presented in Chapter 4 and 6. Moreover, two alternative approaches of \ce{WO3} NWs were also attempted, and the seeded growth method proved effective for large scale growth.

### 2014-10-02 misc/mwe.tex
after format review, bold font in figure caption removed, frontmatter spacing fixed

* remove all bold font, including figure captions, hypothesis env
* abstract; after skip line number is 2, title capital the first letter only
* section after skip none
* no external link in electronic version, turn off doi
*

>>>>

* remove all bold font, including figure captions, hypothesis env
* abstract; after skip line number is 2, title capital the first letter only
* section after skip none
* no external link in electronic version, turn off doi
* adjusting space between list of fig tbl, in tocloft afterskip command

`a ref <https://staff.washington.edu/fox/tex/uwthesis.shtml>`_
